Six ways to understand monads\\ \small{Experiences from the functional programming course at TU Delft}

### 2012-11-01 latex/paper.tex
Fix paper formatting

\author{\IEEEauthorblockN{Erik Meijer}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{
Delft University of Technology\\
Delft, The Netherlands\\
Email: {H.J.M.Meijer, G.Gousios@tudelft.nl} 
}  
}
\maketitle

@@

  In the last few years, the popularity of functional programming as a way of
  solving computational problems has increased significantly. While most
  computer science curricula do include a course on functional programming, in
  many cases it is disconnected from practical applications, which is
  precisely where functional programming shines. To fill in this gap, we
  designed a functional programming course that demanded from students to
  learn by experience with real world applications. In this work, we present
  our experiences with conducting this course.

@@

>>>>

\author{\IEEEauthorblockN{Erik Meijer and Georgios Gousios}
\IEEEauthorblockA{
Delft University of Technology\\
Delft, The Netherlands\\
Email: \{h.j.m.meijer, g.gousios\}@tudelft.nl
}
}
\maketitle

@@

  In the last few years, the popularity of functional programming as a way of
  solving computational problems has increased significantly. While most
  computer science curricula do include a course on functional programming, in
  many cases it is disconnected from practical applications, which is
  precisely where functional programming shines. To fill in this gap, we
  designed a functional programming course that  required students to
  learn by experience with real world applications. In this paper, we present
  the course's design and outline our experience from delivering it.

@@

\begin{IEEEkeywords}
functional programming, teaching
\end{IEEEkeywords}
